Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-13 icse/paper.tex
Is this better?

\begin{abstract}
Duplication in source code is often seen as one of the most harmful types of technical debt, because it increases the size of the codebase and creates implicit dependencies between fragments of code. To remove such antipatterns, a developer should refactor the codebase. There are many tools that assist in this process. However, these are limited to measuring the size of clones to determine whether they should be considered. Because of this, the output of such tools is often of limited assistance to the developer in the refactoring process.

We propose method and tool for the detection and automated refactoring of clones. We use this tool on a corpus of open source Java systems. We use a set of metrics to determine the impact of the applied refactorings to the maintainability of the systems. These metrics are system size, cyclomatic complexity, duplication and number of method parameters. On basis of these results, we decide which clones improve system design and thus should be refactored.

We identified a set of four factors that influence the maintainability impact of clones. The first is the size of the clone. The second is the relation between the code fragments in a clone. The third is whether the clone fragments create, modify or return data. The fourth is the amount of data that cloned fragments use. By using these four factors, we can suggest only clones that will improve maintainability when refactored and prioritize them accordingly.
\end{abstract}

>>>>

\begin{abstract}
Duplication in source code is often seen as one of the most harmful types of technical debt, because it increases the size of the codebase and creates implicit dependencies between fragments of code. To remove such antipatterns, a developer should refactor the codebase. There are many tools that assist in this process. The thresholds and prioritization of the clones detected by such tools can be improved by considering the maintainability of the codebase after a detected clone would be refactored.

We propose method and tool for the detection and automated refactoring of clones. We use a set of metrics to determine the impact of the applied refactorings to the maintainability of the systems. These metrics are system size, cyclomatic complexity, duplication and number of method parameters. On basis of these results, we decide which clones improve system design and thus should be refactored. We identified a set of four factors that influence the maintainability impact of clones. The first is the size of the clone. The second is the relation between the code fragments in a clone. The third is whether the clone fragments create, modify or return data. The fourth is the amount of data that cloned fragments use. By using these four factors, we can suggest only clones that will improve maintainability when refactored and prioritize them accordingly.

Given these maintainability influencing factors and their effect on the source code, we measure their impact over a large corpus of open source Java projects. This results in a set of thresholds by which clones can be found that should be refactored to improve system maintainability.
\end{abstract}
